Regularising Lotka--Volterra interaction matrices by species grouping: optimal groupings are unpredictable

### 2021-10-24 article.rnw
Add the Acknowledgements.
Centre the coclassification matrix subfigures.
They had somehow become left aligned, possibly with the use of endfloat.

\pgfplotsset{%
	colormap={coclassification}{color=(white) color=(red)}
}
\colorlet{coclassification diagonal}{black!20}
\begin{figure}
	\centering
	\begin{subfigure}{\textwidth}
		<<echo=FALSE>>=
			weighted_coclassification_kable(
				brute_data$weighted_col_coclassification_matrix,
				colourmap="coclassification", diagonal_colour="coclassification diagonal"
			)
		@
		\caption{Weighted coclassification of competitive effects (columns of the interaction matrix).}
		\label{fig:coclassification-cols}
	\end{subfigure}

@@

	\begin{subfigure}{\textwidth}
		<<echo=FALSE>>=
			weighted_coclassification_kable(
				brute_data$weighted_row_coclassification_matrix,
				colourmap="coclassification", diagonal_colour="coclassification diagonal"
			)
		@
		\caption{Weighted coclassification of competitive responses (rows of the interaction matrix).}
		\label{fig:coclassification-rows}
	\end{subfigure}

@@

>>>>

\pgfplotsset{%
	colormap={coclassification}{color=(white) color=(red)}
}
\colorlet{coclassification diagonal}{black!20}
\begin{figure}
	\centering
	\begin{subfigure}{\textwidth}
		\centering
		<<echo=FALSE>>=
			weighted_coclassification_kable(
				brute_data$weighted_col_coclassification_matrix,
				colourmap="coclassification", diagonal_colour="coclassification diagonal"
			)
		@
		\caption{Weighted coclassification of competitive effects (columns of the interaction matrix).}
		\label{fig:coclassification-cols}
	\end{subfigure}

@@

	\begin{subfigure}{\textwidth}
		\centering
		<<echo=FALSE>>=
			weighted_coclassification_kable(
				brute_data$weighted_row_coclassification_matrix,
				colourmap="coclassification", diagonal_colour="coclassification diagonal"
			)
		@
		\caption{Weighted coclassification of competitive responses (rows of the interaction matrix).}
		\label{fig:coclassification-rows}
	\end{subfigure}

@@

\section*{Acknowledgements}

I thank Daniel B. Stouffer for advice throughout the study, and particularly for making me aware of Akaike weights and suggesting the use of coclassification matrices.
